### 2023-04-21 paper/content.tex
Fix citations to software
Many of the bibtex items were incorrect.

The image re-scaling and blob detection through the Laplacian of Gaussian method was performed with the scikit-image library \citep{VanderWalt2014}. 
We also used matplotlib \citep{Hunter2007} for plotting the figures and mplstereonet \citep{mplstereonet} for stereograms. 
Basic calculations were performed using Numpy \citep{Harris2020} and Scipy \citep{2020SciPy-NMeth}. 
Verde \citep{verde2018} was used to generate data grids and to perform the regional residual separation, while the upward continuation filter was calculated using Harmonica \citep{harmonica2020}. 
The Choclo library \citep{choclo2022} provided kernel functions utilized in the forward and inverse problems. 
The Numba just-in-time compilation library \citep{lam2015numba} was used to speed-up calculations. 
Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful tool for working with multi-dimensional datasets allowing an easy way of data visualization and extraction with advanced indexing techniques.

>>>>

The image re-scaling and blob detection through the Laplacian of Gaussian
method were performed with the scikit-image library \citep{VanderWalt2014}.
We also used matplotlib \citep{Hunter2007} and mplstereonet \citep{mplstereonet}
or generating figures and stereograms.
Basic calculations were performed using Numpy \citep{Harris2020} and Scipy
\citep{2020SciPy-NMeth}.
Verde \citep{verde2018} was used to generate data grids.
Upward continuation was performed using Harmonica \citep{harmonica2020}.
The Choclo library \citep{choclo2022} provided kernel functions used in the
forward and inverse problems.
The Numba just-in-time compilation library \citep{lam2015numba} was used to
speed-up calculations.
Lastly, the Xarray library \citep{hoyer2017xarray} offered a fast and powerful
tool for working with multi-dimensional datasets allowing an easy way of data
visualization and extraction with advanced indexing techniques.
